---
title: "WUP_04"
author: "Saul Perez Ramos"
date: "Summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
GSScsv <- read.csv("GSScsv.csv")

```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(GSScsv,aes(x=DEGREE,y=WORDSUM))

basicCN + geom_boxplot()
```

The graph shows that there is a difference in wordsum test scores between grade levels. The LT

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=GSScsv)
```

The people that have a a degree from junior college the minimum is at least twice as much as the other categories. In the quarter 3 bachelor, graduate an junior college have a shared space

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
model1 <- aov(WORDSUM~DEGREE,data=GSScsv)
summary.aov(model1)
```

The chances of getting results like this if there was no difference between subgroups is 2.36 out of 10,000.This leads us to believe there is a difference in the test scores between subgroups.

Now that we have a low P value we want to see what values are different from one another. We will us tukey hsd to find that.

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 16, 2, 2))
plot(TukeyHSD(model1),las=2)
```
We have two sets that are different. Highschool is different than graduates and LT highschool is different than graduate. You will always get negative values when comparing those two.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In conclusion there is a difference between graduates and highschool. As well as LT highscool compared to graduate. 